% -*- mode:flyspell; mode:latex -*-
\documentclass[12pt]{article}
\addtolength{\oddsidemargin} {-0.885in}
\addtolength{\textwidth}{1.75in}
\addtolength{\evensidemargin}{-0.8in}


\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{float}
%% \usepackage{siunitx}

%% \usepackage{gensymb}


\usepackage{tikz}
\usepackage{[caption}
\usetikzlibrary{arrows}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
% \usepackage[absolute,overlay]{textpos}
% \usepackage{onimage}

\usepackage{tabularx}
\usepackage{times}
\usepackage{graphics}

% \usepackage{subfigure}
% \usepackage{scalefnt}
%
% \renewcommand\thesubfigure{\arabic{subfigure}}

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{hhline}
\usepackage{subfig}
\usepackage{color}
\usepackage[all]{hypcap}

\usepackage[normalem]{ulem}  % for striking out
\usepackage{soul}
% \usepackage{fancyhdr}
% \pagestyle{fancy}
% \fancyhead[C]{}
% \fancyhead[L] {\it{Mu2e-doc-29670-v1.0} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% use natbib - biblatex not available on Mu2e interactive nodes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[square,sort,comma,numbers]{natbib}

% location of the .bib files: env var BIBINPUTS (~/library/bibliography)

% \usepackage[backend=biber, style=numeric-comp, sorting=ynt] {biblatex}
% \addbibresource{clfv.bib}

% \addbibresource{stntuple.bib}
% \addbibresource{mu2e_web.bib}
% \addbibresource{radiative_pion_capture.bib}

\graphicspath{{figures/}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% for portability, make sure all commands are included locally,
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{ForestGreen}{RGB}{20,109,20}
\include{local_commands}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% for editors
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand {\pasha}[1]     {{\green  #1}}
\newcommand {\simon}[1]     {{\blue   #1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{titlepage}
  \begin{flushright}
    \bf {MU2E/PHYSICS/50071} \\
    version 1.02
    \today
 \end{flushright}

  \vspace{1cm}

  \begin{center}
    {\Large \bf MIDAS+ARTDAQ-based data acquisition system for Mu2e
      \vspace{0.3in}
    }

    \vspace{1cm}
    S.Corrodi(ANL), P.Murat(FNAL), ...

    % \footnote{\texttt{Fermilab; e-mail: murat@fnal.gov}}
    \vspace{0.3cm}

    \vspace{0.8cm}
  \end{center}

  \begin{abstract}
    \vspace{0.2in}

    This document describes a solution for the Mu2e data acquisition
    system based on MIDAS+ARTDAQ {\red should there be a name? }.

    It has been prototyped and tested by several Mu2e
    detector groups. 

    We propose to exercise this solution and demonstrate
    its functionality in the upcoming GR4.
  \end{abstract}

\end{titlepage}
% \frontmatter
% \chapter*{Abstract}
%
% \addcontentsline{toc}{chapter}{Abstract}
%
% \mainmatter
%
{\tableofcontents}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\chapter{Calibration}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{input_data}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section {Revision History and TODO items}

\begin{itemize}
\item
  v1.01: version for internal review
\end{itemize}

% {\red
% TODO items:
% 
% \begin{itemize}
% \item
% \end{itemize}
% }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section {Executive Summary}

Development of the Mu2e DAQ has been lagging behind for quite significant time.
Despite some recent progress, after years of trying no Mu2e collaborator
can operate the DAQ system in their own. With a few months left before the start of the
cosmic run, the system has missing pieces which are yet to be designed.
%
The core of the DAQ system, OTSDAQ, has not been used before by any running experiment.
In is complicated and undocumented. The interfaces between different parts are not
specified, and its complexity and lack of modularity create a very high entry
threshold for the Mu2e collaborators.
%
Most of the DAQ development is happening outside the collaboration which has very
limited input into the development process.
%
During the data taking, the collaboration will have to operate the DAQ system
and it will have to be functional 24x7. In our view, the cost of operating 
and supporting the present DAQ system, expressed in terms of the lost beam time,
will be too high.

% 
We have therefore developed and prototyped a DAQ system based on the combination of two
packages, ARTDAQ \cite{2017_ARTDAQ_Biery} and MIDAS \cite{2025_MIDAS_WIKI}.
%
ARTDAQ is a distributed trigger farm software developed at Fermilab and previously
used by several Fermilab neutrino experiments. 
%
MIDAS is a full DAQ suite which has been used for about 30 years by many HEP experiments
at PSI, TRIUMF, CERN, KEK. It should be noted that MIDAS has also been used
by the g-2 experiment at Fermilab.
%
Out of the currently running experiments, MIDAS is currently used by MEG-II which,
as Mu2e,  searches for CLFV. Another CLFV experiment, Mu3e, which DAQ hardware architecture
is rather close to that of Mu2e, will also be using a MIDAS-based DAQ system.
In a way, MIDAS became a de-facto DAQ standard for small and medium scale HEP
experiments.

Any DAQ system at its early stages has many issues which can only be uncovered and fixed
by operating it. MIDAS has been debugged and tuned by tens of experiments
and by decades of the running time. Although the initial design of MIDAS goes 30 years back,
its architecture is advanced, and the software infrastructure is constantly updated
to use modern technologies.

Based on our technical assessment, a system, which combines the power of
the distributed ARTDAQ data processing with the strength of the integrated
MIDAS-based run control and monitoring, provides the best technical solution
for the Mu2e DAQ.
%
Adding to that, many Mu2e collaborators already have operational experience with
the MIDAS-based DAQ. New collaboration members, coming to Mu2e from other muon 
experiments will likely know MIDAS.

The following sections describe the architecture of the proposed system,
its interfaces, and the status of the present implementation.

\include{system_architecture}
\include{daq_configuration}
\include{detector_configuration}
% \include{artdaq_interface}
\include{runtime_diagnostics}
\include{operations}
\include{support}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section {Summary}

\begin{itemize}
\item 
  The MIDAS+ARTDAQ solution for the Mu2e DAQ has been extensively prototyped.
\item
  the solution is significantly simpler for both the users and the developers
\item
  its current functionality, in many respects, already exceeds that
  of the current OTSDAQ-based system  
\item
  collaboration members, including students, are contributing
  to the development process. 
\item
  new collaboration members joining Mu2e from other muon experiment will
  likely have an experience of operating a MIDAS-based DAQ
\end{itemize}

Based on our assessment, a combination of MIDAQ and  ARTDAQ
provides the best solution for the Mu2e DAQ.

We therefore propose to exercise this solution and demonstrate
its functionality in the upcoming GR4.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliographystyle{unsrtnat}
\bibliography{clfv,mu2e_internal_notes,daq}

% \include{appendix_a}
\include{appendix_b}

\end{document}
